---
output:
  html_document:
    keep_md: yes
resource_files:
- README.html
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# My work on r2dii packages

Adapted from https://rpubs.com/hadley/gh.

On July 1, 2019 I started working on an ecosystem of R packages named "r2dii". Here I explore my work so far.

```{r}
library(gh)
library(purrr)
library(tibble)
library(dplyr)
library(readr)
library(lubridate)
library(ggplot2)
library(forcats)
```

I start by getting a list of the 50 repos that I’ve touched most recently.

```{r}
my_repos <- function(type = c("all", "owner", "public", "private", "member"), 
                     limit = 50) {
  type <- match.arg(type)
  
  gh(
    "GET /user/repos",
    type = type, 
    sort = "updated",
    .limit = limit
  )
}
repos <- my_repos("owner", limit = 50)
length(repos)

full_name <- repos %>% map_chr("full_name")
head(full_name, 20)
```

(If you’re doing this yourself, you’ll need to make sure you’ve set up an environment variable GITHUB_PAT with a GitHub personal access token.)

And then, for each repo, I get all the commits since 2019-07-01, around the time I became a full time software developer. I collaborate with other people, so I make sure to extract the author of the commit.

```{r}
repo_commits <- function(full_name, since = "2019-07-01") {
  message("Requesting commits for ", full_name)
  
  commits <- gh("GET /repos/:full_name/commits", 
    full_name = full_name, 
    since = since,
    .limit = Inf
  )
  
  if (length(commits) == 0) {
    return(NULL)
  }
  
  tibble(
    full_name = full_name,
    author = commits %>% map_chr(c("author", "login"), .null = NA_character_),
    datetime = commits %>% map_chr(c("commit", "author", "date"), .null = NA_character_)
  )
}

commits <- full_name %>% map(repo_commits) %>% compact() %>% bind_rows()
commits
```

Next, I parse the commit date, and set my timezone. I break the datetime into separate date and time pieces as that will make plotting easier later on.

```{r}
commits <- commits %>% mutate(
  datetime = lubridate::with_tz(readr::parse_datetime(datetime), "America/Chicago"),
  date = floor_date(datetime, "day"),
  time = update(datetime, yday = lubridate::yday("2019-08-01"))
)
commits
```

Next, I do a couple of quick checks to make sure the data looks reasonable.

```{r}
commits %>% count(full_name, sort = TRUE) %>% print(n = 20)

commits %>% count(author, sort = TRUE)
```

Now I pull out just the commits that I made, and only for repositories matching "r2dii".

```{r}
mauro <- commits %>% 
  filter(author == "maurolepore", grepl("r2dii", full_name))

mauro
```

To start, lets figure out what I’ve been working on. I’ll just look at the top 25 repos.

```{r}
mauro %>% 
  mutate(repo = full_name %>% fct_reorder(date) %>% fct_rev() %>% fct_lump(25)) %>% 
  ggplot(aes(date, repo)) + 
  geom_jitter()
```

What times of day do I usually work on things?

```{r}
mauro %>% 
  ggplot(aes(date, time)) + 
  geom_jitter()
```

We can look at my average work week by breaking down by day of week.

```{r}
mauro %>% 
  mutate(wday = wday(date, label = TRUE) %>% fct_shift(1) %>% fct_rev()) %>% 
  ggplot(aes(time, wday)) + 
  geom_jitter()
```

How much time have I spent working on each project?

```{r}
hours_spent <- mauro %>% 
  group_by(date, full_name) %>% 
  arrange(datetime, full_name) %>% 
  mutate(time_spent = last(time) - first(time)) %>% 
  select(full_name, date, time_spent) %>% 
  unique() %>% 
  ungroup() %>% 
  group_by(full_name) %>% 
  summarize(hours_spent = sum(time_spent, na.rm = TRUE)) %>% 
  arrange(desc(hours_spent)) %>% 
  mutate(
    hours_spent = as.double(hours_spent) / 3600,
    # Rest lunch (~1 hour every 8 hours)
    hours_spent = hours_spent - (hours_spent %/% 8)
  )
hours_spent
```

How many expected work hours have I accumulated so far?

```{r}
days <- as.double(today() - date("2019-07-01"))
weekend_days <- (days %/% 7) * 2
work_days <- days - weekend_days
work_hours <- work_days * 8
work_hours
```

What percent of my time goes to r2dii packages?

```{r}
work_on_r2dii <- sum(hours_spent$hours_spent)
percen_work_on_r2dii <- work_on_r2dii / work_hours * 100
percen_work_on_r2dii
```


